---
title: "Assignment3 - R Character Manipulation"
author: "Peter"
date: "9/11/2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
# Introduction

This assignment deals with string manipulation below are 4 exercises
```{r}
library(DT)
library(stringr)
```
### Exercise 1

1. Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"

#### Answer

```{r}

majors <- read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/2d2ff3e9457549d51f8e571c52099bfe9b2017ad/college-majors/majors-list.csv")
filtered <- majors$Major %>% str_subset("DATA|STATISTICS")
filtered
```
### Exercise 2

2. Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

#### Answer


```{r warning=FALSE}
str <- '[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"

[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  

[9] "elderberry"   "lime"         "lychee"       "mulberry"    

[13] "olive"        "salal berry"'
str2 <- str_extract_all(str,pattern = '[A-Za-z]+.?[A-Za-z]+')
vect <- str_c(str2, collapse = ", ")
writeLines(vect)
```
### Exercise 3

3. Describe, in words, what these expressions will match:


i) (.)\1\1

#### Answer


Match any character appearing 3 times in a row
```{r}
sample <- c("Awww","Hmmm","lol")
str_view(sample,"(.)\\1\\1")
```

ii) "(.)(.)\\2\\1"

#### Answer


Match any words pair of characters followed by same pair of character is reversed order  
```{r}
sample <- c("noon","teeth")
str_view(sample,"(.)(.)\\2\\1")
```


iii) (..)\1

#### Answer


Matches a pair of characters which has a repetition of same pair
```{r}
sample <- c("dada","haha")
str_view(sample,"(..)\\1")
```
iv)"(.).\\1.\\1"

#### Answer


Match a expression which has - a character followed by any character then the same character as initial character then again any character ended by the same as first character
```{r}
sample <- c("abaha")
str_view(sample,"(.).\\1.\\1")
```


v) "(.)(.)(.).*\\3\\2\\1"

#### Answer


Match any expression which are in - 3 characters followed by 0 or more characters then followed by 3 characters of the start in reverse order

```{r}

sample <- c("momismom")
str_view(sample,"(.)(.)(.).*\\3\\2\\1")
```

### Exercise 4

4) Construct regular expressions to match words that:

i)Start and end with the same character.

#### Answer


```{r}
str_view(c("dad","settings","day"),"(.).*\\1")
```


ii) Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)

#### Answer


```{r}
str_view(c("church","joggingg"),"(..).*\\1")
```


iii)Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)

#### Answer


```{r}
str_view(c("deleven","five"),"(.).*\\1.*\\1")
```

